\documentclass[t, 11pt]{beamer}
\pdfmapfile{+sansmathaccent.map}
%%% Работа с русским языком
\usepackage{cmap}				
\usepackage{mathtext} 				
\usepackage[T2A]{fontenc}		
\usepackage[utf8]{inputenc}			
\usepackage[english,russian]{babel}	

\usetheme{Ilmenau}
\usecolortheme{lily} % Цветовая схема



%%% Работа с картинками
\usepackage{graphicx}

\usepackage{csquotes}

\hypersetup{				
	colorlinks=true,       	
	linkcolor=blue,          
	citecolor=black,       
	filecolor=magenta,      
	urlcolor=red           
}


\title{NLP intro}
\subtitle{...and it's applications}
\author{Чувакин Сергей}
\date{\today}
\institute[<<Анализ больших данных в бизнесе, экономике и обществе>>]{<<Высшая школа экономики>>}

\begin{document}
	\frame[plain]{\titlepage}
	\section{Outline}
	
	\begin{frame}
		\frametitle{\insertsection} 
		\begin{block} {}
			 
			\hyperlink{hist}{\beamerbutton{Breif history}}
		\end{block}
		\begin{block}{}
			\hyperlink{steps}{\beamerbutton{Steps for processing}}
		\end{block}
		\begin{block}{}
			\hyperlink{lm}{\beamerbutton{Language models}}
		\end{block}
		\begin{block}{}
			\hyperlink{sents}{\beamerbutton{Sintiments and topics}}
		\end{block}
			\begin{block}{}
		\hyperlink{chatbots}{\beamerbutton{Chatbots}}
		\end{block}
	\end{frame}
	
	\subsection{NLP per se}
	\begin{frame} \label {hist}
		\frametitle{\insertsection} 
		\frametitle{\insertsubsection} 
		\begin{itemize}
			\item 1900s Saussure
			\item 1950s Turing 
			\item 1957s Chomsky
			\item 1966 - 1980ss ai winter
			\item 1990s $\sim$ n-grams, lstm, language models, etc.
		\end{itemize}
	\end{frame}
	\subsection{NLP tasks} \label{}
	
	\begin{frame}
		\frametitle{\insertsection}
		\frametitle{\insertsubsection}  
	\begin{itemize}
    \item \textbf{Content Categorization:} A linguistic document summary that includes content alerts, duplication detection, search, and indexing.
	\item \textbf{Topic Discovery and Modeling:} Captures the themes and meanings of text collections, and applies advanced analytics to the text.
	\item \textbf{Contextual Extraction:} Automatically pulls structured data from text-based sources.
	\item \textbf{Sentiment Analysis:} Identifies the general mood, or subjective opinions, stored in large amounts of text. Useful for opinion mining.
	\vspace{1cm}
 	\href{https://www.dataversity.net/a-brief-history-of-natural-language-processing-nlp/}{click here}.
 \end{itemize}
	\end{frame}

	\begin{frame}
	\frametitle{\insertsection}
	\frametitle{\insertsubsection}  
	\begin{itemize}

		\item \textbf{Text-to-Speech and Speech-to-Text Conversion:} Transforms voice commands into text, and vice versa.
		\item \textbf{Document Summarization:} Automatically creates a synopsis, condensing large amounts of text.
		\item \textbf{Machine Translation:} Automatically translates the text or speech of one language into another.
		
		\vspace{1cm}
		\href{https://www.dataversity.net/a-brief-history-of-natural-language-processing-nlp/}{click here}
	\end{itemize}
\end{frame}


	\subsection{Processing steps}

\begin{frame}\label{steps}
	\frametitle{\insertsection}
	\frametitle{\insertsubsection}
	\begin{itemize}
		\item data obtaining 
		\item stemming\textbackslash lemmatization
		\item vectorization (bow, tf-idf, word2vec) 
		\item modeling 
	\end{itemize}
\end{frame}

	
	\subsection{Language models}
	
	\begin{frame}\label{lm}
		\frametitle{\insertsection}
		\frametitle{\insertsubsection}
		Probability of word given the previous.
		\begin{itemize}
			\item Probabilistic models 
			\item RNN, LSTM 
			\item word2vec 
			
			\vspace{1cm}
		\end{itemize}
	\end{frame}
	
	\subsection{Sintiments and topics}
	\begin{frame}\label{sents}
		\frametitle{\insertsection}
		\frametitle{\insertsubsection}
		\begin{itemize}
			\item Text classification.
			\item Recommendation Systems.
			\item Uncovering Themes in Texts. 
		\end{itemize}
	\end{frame}

		\subsection{Chatbots}
	\begin{frame}\label{chatbots}
		\frametitle{\insertsection}
		\frametitle{\insertsubsection}
		\begin{itemize}
			\item Goal-oriented (FAQ bot).
			\item Convesational (Алиса, Siri).
			\item NLU + text generation. 
		\end{itemize}
	\end{frame}

	
	
\end{document}